First Order Alternation

### 2018-11-06 quantifiers/body.tex
ok

We describe applications of this semi-algorithmic method to several
undecidable but recursively enumerable problems, for which no
effective method exist, to date: inclusion between recognizable timed
languages \cite{AlurDill94} and between languages recognized by
finite-memory automata \cite{KaminskiFrancez94}, as well as emptiness
of predicate automata, a model of first-order alternating automata
used to check safety and liveness properties of parameterized
concurrent programs \cite{Farzan15,Farzan16}.

@@

>>>>

As applications of first order alternating automata, we identified
several undecidable but recursively enumerable problems, for which no
effective methods exist, to date: inclusion between recognizable timed
languages \cite{AlurDill94} and between languages recognized by
finite-memory automata \cite{KaminskiFrancez94}, as well as emptiness
of predicate automata, a model of first-order alternating automata
used to check safety and liveness properties of parameterized
concurrent programs \cite{Farzan15,Farzan16}.

@@

\section{Experimental Results}
